mathml: Translate R expressions to MathML and LaTeX/MathJax

### 2022-12-29 Draft3.Rmd
t dist

```{r base-stats, echo=FALSE}
op1 <- list(
  sin=quote(sin(x)),
  cosh=quote(cosh(x)),
  tanpi=quote(tanpi(alpha)),
  log=quote(log(p)),
  log1p=quote(log1p(x)),
  exp=quote(exp(x)),
  expm1=quote(expm1(x)),
  lchoose=quote(lchoose(n, k)),
  sqrt=quote(sqrt(x)),
  mean=quote(mean(X)["A"]),
  absolute=quote(abs(x)))
m1 <- lapply(op1, FUN=mathout, flags=list(cat=FALSE))

@@

op2 <- list(
  sin=quote(sin(x)),
  cosh=quote(cosh(x)),
  tanpi=quote(tanpi(alpha)),
  log=quote(log(p)),
  log1p=quote(log1p(x)),
  exp=quote(exp(x)),
  expm1=quote(expm1(x)),
  lchoose=quote(lchoose(n, k)),
  sqrt=quote(sqrt(x)),
  mean=quote(mean(X)["A"]),
  absolute=quote(abs(x)))
m2 <- lapply(op2, FUN=mathout, flags=list(cat=FALSE))

>>>>

```{r base-stats, echo=FALSE}
op1 <- list(
  sin=quote(sin(x)),
  cosh=quote(cosh(x)),
  tanpi=quote(tanpi(alpha)),
  log=quote(log(p)),
  log1p=quote(log1p(x)),
  exp=quote(exp(x)),
  expm1=quote(expm1(x)),
  lchoose=quote(lchoose(n, k)),
  sqrt=quote(sqrt(x)),
  mean=quote(mean(X)),
  absolute=quote(abs(x)))
m1 <- lapply(op1, FUN=mathout, flags=list(cat=FALSE))

@@

op2 <- list(
  dbinom=quote(dbinom(k, N, pi)),
  pbinom=quote(pbinom(k, N, pi)),
  qbinom=quote(qbinom(p, N, pi)),
  dnorm=quote(dnorm(x)),
  dnorm=quote(dnorm(x, mu, sigma)),
  pnorm=quote(pnorm(x)),
  pnorm=quote(pnorm(x, mu, sigma)),
  qnorm=quote(qnorm(alpha/2L)),
  pchisq=quote(1-pchisq(x, df)),
  qchisq=quote(qchisq(1L-alpha, df)),
  pt=quote(pt(t, N-1L)),
  qt=quote(qt(alpha/2L, N-1L)))
m2 <- lapply(op2, FUN=mathout, flags=list(cat=FALSE))
